Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-03 paper/galsize_paper.tex
Reworked section 5.2

Our treatment of satellite-specific mass loss with the $\mstar+$stripping model is only approximate, because we have  modified the size of satellites without self-consistently modifiying their total stellar mass. In the present work, we have opted not to develop and fine-tune a more complex, semi-analytic model; instead, we have made a simple estimate for the level at which satellite-specific stripping impacts the two-point function.

%Explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are specific to post-infall physics. One obvious possibility that could lead to satellites being smaller than centrals of the same $\mhalo$ is tidal stripping: satellite $\mstar$ could decrease after infall, reducing the size of the galaxy. We have quantitatively tested this possibility with the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}. Comparing the clustering ratios of the ``$\rvir-$based" and ``$\rvir+$stripping" models in Figure \ref{fig:strippingorphans}, we find that the impact of physically motivated levels of satellite mass loss cannot explain the $\rhalf-$dependent clustering seen in SDSS. As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.

%Both the $\rvir-$based model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall. For these models the story is very different: the influence of pre-infall co-evolution has a dramatic impact on $\rhalf-$clustering ratios, with a scale- and $\mstar-$dependence that closely resembles the SDSS signal. Quantitative constraints on the true level of this co-evolution effect will be a natural outcome of the program described in \S\ref{subsec:future}, but it is already clear that the long term co-evolution of galaxy and halo profiles should be considered a critical ingredient to models for the distribution of galaxy sizes across the cosmic web.

>>>>

Physical explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are post-infall and satellite-specific. The success of the $\rvir-$based model, together with the failure of the $\mstar$+stripping model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite. The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS. As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.

While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass. In the present work, we have opted not to develop and fine-tune a complex, semi-analytic model; instead, we have made a simple ``first-order" estimate for the level at which satellite-specific stripping impacts the two-point function. Our findings support the idea that the small sizes of satellites arise primarily from the satellite's distinctive evolution within a high density region and a steep tidal field {\em prior} to becoming a present-day satellite.
